HERMES: Hybrid Error-corrector Model with inclusion of External Signals for nonstationary fashion time series

### 2023-07-09 tmlr_submission/hermes_paper_revision/answers_reviewer_3.tex

We would like to thank the reviewer for the appreciation of the paper and the constructive feedback. We have carefully considered all comments and we will propose a revision of the paper accordingly. In the meantime, you can find below detailed responses and an overview of some of the  modifications that will be added in the revised manuscript.

\section*{Detailed responses}

\subsection*{Requested changes:}
\begin{itemize}
	\item {\em ``The reliability of the data is important for the use of this data by third parties. Please explain in detail how the human processing was done. Also, to what extent can machine failures be included in image processing ? Do humans correct them ?''} \medskip

	\textbf{Author response:} We thank the referee for this remark. Regarding the data-acquisition pipeline presented in Section 2, the human actions are limited. The only human processing comes at the step where the fashion trends are defined. The features are automatically detected by the vision recognition models. Then, we only define trends that are relevant for the fashion industry. For instance, the Mini A-line dress fashion trend is identified where the dress category is detected with a particular shape and a particular length, all of these details detected with different models. These associations of fine-grain attributes are defined by a team of fashion experts and are not provided with the paper.

Concerning the machine failures, all the visual recognition models used to build the proposed dataset have been trained with a standard process involving a train, a eval and a test set. 
Thus, models showing poor performance in terms of accuracy and recall on the test set have been dismissed. No additional human correction has been done. In the proposed paper, we focus on time series prediction so this has a limited impact on our claims. Of course improving visual recognition models would modify slightly the dataset but the time series  prediction challenges would remain similar.

Please note that the data acquisition pipeline has been detailed and extended in Section 2. \\

@@

	\item {\em ``In publishing the data, it would be good to add a little more analysis of the characteristics of the data. For example, basic statistics for each market, statistics for the Weak signal $w^{f,i}_t$, etc.''} \medskip

	\textbf{Author response:} We agree with the referee and we acknowledge that we have not sufficiently presented the diversity of behaviours hidden in the proposed fashion dataset. So as to improve this point, a new section is added in the appendix of the revised version of the paper where 4 different sub-samples of time series are defined and studied separately. \\

@@

	\item {\em ``It is written that represents the index of fashion trends, but it is unclear what exactly it refers to. Does it correspond to a product/item?''} \medskip

	\textbf{Author response:} We understand this remark and further information has been added in the revised paper to clarify this point. The index of fashion trends represents the name of a fashion clothing relevant for the fashion industry. It can be just one attribute detected by a visual recognition model (ex: the Sneakers) but it can also be a combination of several attributes (ex: the Slim Sole Retro Basketball Sneakers). As the fashion trends names are anonymized in the proposed dataset, the architecture used to define the fashion trends is not presented in this paper.\\

@@

	\item {\em ``I didn't know what statistic was $\hat{y}^{c,g,m}$. Could you please explain it in detail?''} \medskip

	\textbf{Author response:} We are not sure of the notation in the question of the referee, in the paper we introduce $\bar{y}^{c,g,m}$ and $\Tilde{y}^{c,g,m}$ but not $\hat{y}^{c,g,m}$. We present below a explanation of the two statistic $\bar{y}^{c,g,m}$ and $\Tilde{y}^{c,g,m}$:
	\begin{itemize}
	\item $\Tilde{y}^{c,g,m}$ is the time series representing the behaviour of the global cloth type $c$ for the gender $g$ on the market $m$. It can be for example the time series representing the evolution of the general pants for females in Europe. The sequence $\Tilde{y}^{c,g,m}$ is then used to normalize each time series $y^{c,g,m,j}$ with the same $c$, $g$ and $m$. All the fashion trends of pants for females in Europe are normalized by the time series representing the general pants for females in Europe.
	\item $\bar{y}^{c,g,m}$ is the time series $\Tilde{y}^{c,g,m}$ where the seasonality component has been removed. The seasonality component is removed as we only want to remove social media bias with the normalization step and not remove or change the seasonality of the proposed fashion trends.
	\end{itemize}	
Additional information (regarding the Jersey Top normalization example) has been added at the end of Section 2.2 and in the legend to Figure 3.

@@

	\item {\em ``It may be a good idea to modify the structure of Section 3. It is better to explain the hybrid model (4) at first.  Then, elaborate on the motivation behind the formulation of (4). The output of the RNN appears to represent the weights in summing $f^n(.)$ and $\bar{y}^n_{T}$. Is that correct? Also, when is one of $y^{pred}$ and $y^{corr}$ more dominant than the other? The cost function described in Section 4.1 should be moved to Section 3.''} \medskip

	\textbf{Author response:} We thank the referee for this remark. In the proposed method, $f^n(.)$ represents a time-series-specific parametric model, the model $f^n(y^n_{1:T},\theta^n_{predictor})$ is linked to the time series $y^n_{1:T}$. By contrast, the recurrent neural network denoted $RNN()$ in the paper is global: the same network is used for every time series. It is why we introduce $\bar{y}^n_T$ to rescale inputs and outputs of $RNN()$ as we do not assume that all the time series have the same volume. The fraction of the final prediction due to $y^{pred}$ or $y^{corr}$ is variable and depends on the nature of the time series (and the external signal if it is provided to the corrector model). An illustration is presented in a new section added in the appendix of the revised paper. In this section, we study the accuracy of the HERMES model on sub-samples of time series sharing the same behaviour. On the sub-sample of time series with a high level of noise, predictions of the HERMES model seem to rely only on $y^{pred}$. By contrast, on a sub-sample called 'disrupting trend', we can see that $y^{corr}$ strongly impacts the final prediction resulting in an improvement of the final accuracy of the HERMES model. Concerning the cost function described in Section 4.1, we decided to present this part in the Experiments section and not in the section presenting the model as the choice of the loss function can change depending on the use case. For instance, the L1 loss function was selected to train the HERMES variations on the Fashion dataset while the MASE loss has been used for the M4 dataset.\\

### 2023-07-10 tmlr_submission/hermes_paper_revision/hermes_paper.tex
Update hermes_paper.tex

\textcolor{orange}{
\subsection{Discussion}
Results of the two previous forecasting tasks illustrate that the proposed hybrid method is a general framework, easily adaptable to different use cases and showing remarkable accuracy results able to compete with other state-of-the-art methods. With its neural network component, it is also able to leverage any kind of external signals, which is starting to become essential in more and more forecasting applications. However, the presented method also shows some weaknesses listed above:
\begin{itemize}
\item With the inclusion of a neural network at the end of the framework, the interpretability of the final prediction of the HERMES method is not possible. For instance, the use of the external signal can not be easily assessed and confidence intervals provided by the statistical predictors are no longer valid when they are used in the hybrid framework. A possible idea already studied in the literature is to reverse the order by using first a neural network to compute a set of parameters that is then used by an interpretable model (see for instance the DeepAR model introduced in \cite{salinas2020}.)
\item The proposed hybrid approach can be computationally long to train and to use in inference. Compared to neural-network-based models, the statistical component of the hybrid model has to be retrained for every new time series. For HERMES variations using a complexe statistical predictor like TBATS, this step can be expensive especially on large datasets.
\item In the Fashion use case, the inclusion and use of the external signals by the HERMES model seems to be sub-optimal. For several examples, the external signal starts to burst but the HERMES approach does not use this information to totally change the first parametric prediction and forecast a burst of the main signal. A possible explanation is that the external signals are relevant only in a few fashion time series. Knowing when and how to use them correctly seems to be too difficult for the corrector component part. An ongoing work is to use several neural network models specialized on different uses of the external signals. Then depending on the past of the time series and the external signals, a hidden state could be used to choose which neural network correctors. In addition to bringing more flexibility on the use of the external signals, this promising work could also improve the interpretability of the final prediction depending at which specialized neural network model was chosen in the final prediction.
\end{itemize}
}
\section{Conclusion}
\label{sec:conclusion}
In this paper, we propose a new hybrid model for non stationary time series forecasting. By mixing the performance of local parametric models and a global neural network, \textit{hermes-tbats} clearly outperforms traditional statistical methods and full neural network models on two forecasting tasks. Furthermore, this new model is totally suited to deal with external signals. With a fine pre-processing and a well-designed architecture, the proposed hybrid framework succeeds at leveraging complex extra data and reaches promising accuracy levels. In addition, a fashion dataset gathering a sample of $\numberts$ time series and a collection of weak signals is provided. \textcolor{orange}{We show that it is possible to represent fashion data with time series and introduce statistical models based on social media data.} By making it publicly available, we hope that it will enhance the diversity of datasets for time series forecasting and pave the way for further explorations.
As a possible future work, designing new models for the weak signals would improve their inclusion  in the HERMES architecture. Focusing on the examples with important changes of behaviours, a fine analysis of the impact of the collection of weak signals is the topic of ongoing works. In the same way, an interesting improvement of the hybrid framework can be to introduce not a single but several neural networks trained at correcting different kinds of weaknesses. A perspective is to add a latent discrete label to select dynamically the regime shifts.

>>>>

\textcolor{orange}{
\subsection{Discussion}
Results of the two previous forecasting tasks illustrate that the proposed hybrid method is a general framework, easily adaptable to different use cases and able to compete with other state-of-the-art methods. With its neural network component, it is also able to leverage any kind of external signals, which which could become essential in more and more forecasting applications. The experiments highlight some limitations that may be the topic of future works.
\begin{itemize}
\item In its current form, the use of the neural network prevents the interpretability of the final prediction. The use of the external signal can not be easily assessed and no confidence intervals are provided with the hybrid framework. Future works can focus on designing more intepretable models, using for instance Bayesian neural networks, or combining neural networks with state space models.
\item The proposed hybrid approach can be computationally intensive, for instance  compared to classical neural-network-based models. A solution to improve this limitation is to propose new  procedures to train jointly both parts of the model with mini batches of observations.
%, the statistical component of the hybrid model has to be retrained for every new time series. For HERMES variations using a complexe statistical predictor like TBATS, this step can be expensive especially on large datasets.
\item In the Fashion use case, the inclusion and use of the external signals could be improved as the external signals are relevant only in a few fashion time series. An ongoing work is to use several neural networks specialized on different uses of the external signals. Depending on the past of the time series and the external signals, a hidden state could be used to switch between models.% In addition to bringing more flexibility on the use of the external signals, this promising work could also improve the interpretability of the final prediction depending at which specialized neural network model was chosen in the final prediction.
\end{itemize}
}
\section{Conclusion}
\label{sec:conclusion}
In this paper, we propose a new hybrid model for non stationary time series forecasting. By mixing the performance of local parametric models and a global neural network, \textit{hermes-tbats} clearly outperforms traditional statistical methods and full neural network models on two forecasting tasks. Furthermore, this new model is totally suited to deal with external signals. With a fine pre-processing and a well-designed architecture, the proposed hybrid framework succeeds at leveraging complex extra data and reaches promising accuracy levels. In addition, a fashion dataset gathering a sample of $\numberts$ time series and a collection of weak signals is provided. \textcolor{orange}{We show that it is possible to represent fashion data with time series and introduce statistical models based on social media data.} By making it publicly available, we hope that it will enhance the diversity of datasets for time series forecasting and pave the way for further explorations.
As a possible future work, designing new models for the weak signals would improve their inclusion  in the HERMES architecture. Focusing on the examples with important changes of behaviours, a fine analysis of the impact of the collection of weak signals is the topic of ongoing works. In the same way, an interesting improvement of the hybrid framework can be to introduce not a single but several neural networks trained at correcting different kinds of weaknesses. A perspective is to add a latent discrete label to select dynamically the regime shifts.
